Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-15 paper/paper.tex
Maybe fix propositions
Experimental setup
Reword intro a bit

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs \citep{CP2016MCSPaper}. This is
largely because strong inference, based upon the degrees of vertices
\citep{DBLP:journals/ai/Solnon10} and the distances between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted. In
this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
graph into the target. We then present and evaluate an algorithm which, when $k$ is small (say,
between 1 and 3) is much more scaleable than general maximum common subgraph algorithms.

@@

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\deg(p) \le \deg(t) + k$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $\nds(p)[k+1, k+2, \ldots] \preceq \nds(t)$.
\end{proposition}

>>>>

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs \citep{CP2016MCSPaper}. This is
largely because strong inference, based upon the degrees of vertices
\citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted. In
this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then weakened
forms of degree and path based filterings are still effective in pruning the search space and
providing additional constraints respectively. We then show that combining these techniques does
lead to a practical algorithm which can scale to work with the families of graphs commonly used to
benchmark subgraph isomorphism algorithms.

@@

\subsection{Experimental Setup}

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
\end{proposition}
